Identifying Drawings with the Quick Draw Challenge

### 2018-12-05 report/report_draft.Rmd
add tasks
report started

Our team has based our project idea on the "Quick, Draw!" Kaggle competition 
which classifies user drawings into one of 345 label categories. Many drawings 
were incomplete or failed to match the label. The challenge was to effectively 
build a recognizer that could work with this noisy data. The challenge was unique 
from an algorithmic perspective because the data included both temporal and 
spatial components; areas that have traditionally used two different 
types of Neural Network Architectures. Our team attempted to provide a solution 
using a subset of the data, to the Kaggle problem, while taking a more in depth 
look at potential pitfalls and modeling strategy, without having to use 
extensive computational resources.

@@

First, we got our data from Google/Kaggle. CNNs are traditionally known to work
well with spatial data, which prompted us to process the original csv files to 
images of the drawings.

Maybe we should structure our models as experiments. Then talk 
about what worked the best. Here's some example hypotheses

@@

@@

@@

>>>>

Provide a short background of the project (e.g., what kind of question is to be 
answered with this work). Provide a short non-technical summary of your 
analytical strategy.

Our team has based our project idea on the "Quick, Draw!" Kaggle competition 
which classifies user drawings into one of 345 label categories. Many drawings 
were incomplete or failed to match the label. The challenge was to effectively 
build a recognizer that could work with this noisy data. The challenge was unique 
from an algorithmic perspective because the data included both temporal and 
spatial components; areas that have traditionally used two different 
types of Neural Network Architectures. Our team attempted to provide a solution 
using a subset of the data, to the Kaggle problem, while taking a more in depth 
look at potential pitfalls and modeling strategy, without having to use 
extensive computational resources. With this project, we explore image 
classification in depth. We try out various experiments like fully connected 
neural network vs CNN, bias vs. variance tradeoff, overfitting data purposefully
and trying out techniques like regularization and dropout to fix overfitting and
finally, testing neural network with imbalanced data.

@@

First, let's talk about data collection. Google initially compressed and converted
the images to .npy files. These .npy files are basically 28*28 images, containing
more than 100,000 rows each.

So here are the experiments we performed.

### EDA

We checked the We plotted images from several categories

@@

Try out: Overfitting, Bias/variance, imbalance, dropout, pushing activation

@@

The model built using CNN was better than human accuracy, which was in turn 
better than the model built using fully connected network.

@@

Everyone worked on everything.

### 2018-12-05 report/report_draft.tex
add tasks
report started

Our team has based our project idea on the ``Quick, Draw!'' Kaggle
competition which classifies user drawings into one of 345 label
categories. Many drawings were incomplete or failed to match the label.
The challenge was to effectively build a recognizer that could work with
this noisy data. The challenge was unique from an algorithmic
perspective because the data included both temporal and spatial
components; areas that have traditionally used two different types of
Neural Network Architectures. Our team attempted to provide a solution
using a subset of the data, to the Kaggle problem, while taking a more
in depth look at potential pitfalls and modeling strategy, without
having to use extensive computational resources.

@@

First, we got our data from Google/Kaggle. CNNs are traditionally known
to work well with spatial data, which prompted us to process the
original csv files to images of the drawings.

Maybe we should structure our models as experiments. Then talk about
what worked the best. Here's some example hypotheses

>>>>

Provide a short background of the project (e.g., what kind of question
is to be answered with this work). Provide a short non-technical summary
of your analytical strategy.

Our team has based our project idea on the ``Quick, Draw!'' Kaggle
competition which classifies user drawings into one of 345 label
categories. Many drawings were incomplete or failed to match the label.
The challenge was to effectively build a recognizer that could work with
this noisy data. The challenge was unique from an algorithmic
perspective because the data included both temporal and spatial
components; areas that have traditionally used two different types of
Neural Network Architectures. Our team attempted to provide a solution
using a subset of the data, to the Kaggle problem, while taking a more
in depth look at potential pitfalls and modeling strategy, without
having to use extensive computational resources. With this project, we
explore image classification in depth. We try out various experiments
like fully connected neural network vs CNN, bias vs.~variance tradeoff,
overfitting data purposefully and trying out techniques like
regularization and dropout to fix overfitting and finally, testing
neural network with imbalanced data.

@@

First, let's talk about data collection. Google initially compressed and
converted the images to .npy files. These .npy files are basically 28*28
images, containing more than 100,000 rows each.

So here are the experiments we performed.

\subsubsection{EDA}\label{eda}

We checked the We plotted images from several categories
